---
title: "MID Project"
author: "TEAM SIM"
date: "2023-03-02"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r init, include=TRUE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='asis',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "asis", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

## Data Cleaning and Formating

### Reading the RAW CSV file 
```{r}
#Reading the Raw CSV of IMDB Data Frame
IMDB_raw <- read.csv("imdb_SIM_raw.csv")
summary(IMDB_raw)
```




### Removing the Duplicates
```{r}
# Removing all the duplicate data from the df IMDB
library(dplyr)
IMDB_noduplicates <- distinct(IMDB_raw, Name, .keep_all = TRUE)
write.csv(IMDB_noduplicates, "IMDB_noduplicates.csv")
```

### Heading 2
### Storing the removed duplicates into new CSV file
```{r}
# the duplicated rows that are removed are just stored into a New CSV file just for reference and presentation
dup_idx <- duplicated(IMDB_raw)
dup_rows <- IMDB_raw[dup_idx, ]
dup_rows
write.csv(dup_rows,"IMDB_duplicate_rows.csv")
```
### Calculating the number of missing values
```{r}
sum(is.na(IMDB_noduplicates))
```
### returning the dimensions (number of rows and columns) of the dataset 
```{r}
dim(IMDB_noduplicates)
```

### returning the first six rows of the dataset 
```{r}
head(IMDB_noduplicates)
```

### structure of dataset
```{r}
str(IMDB_noduplicates)
```

###  summarizing the statistical properties of the variables (no duplicates) in the dataset
```{r}
summary(IMDB_noduplicates)
```

### Cleaning and formatting the Rate variable

Rate Variable must be Numeric.Let's Check if "Rate" is Numeric or not `r is.numeric(IMDB_noduplicates$Rate)`

```{r}
# Pulling out the list of non numeric or float values in the "Rate" Variable
non_float_rate <- IMDB_noduplicates$Rate[!is.double(IMDB_noduplicates$Rate)]

# Get unique non-float values in "Rate"
unique(non_float_rate)
```
```{r}

# we see that first row data of Rate is numeric. But lets see how R is reading the same.
class(IMDB_noduplicates$Rate[1])
```
Now that we know from Rate variable it had both float and character data types but R is understanding that other float values are also characters. so lets do two things (1) Removing all the rows with "No Rate" data in IMDB data frame.
                                  (2) Check and convert the Rate variable to float

```{r}
# Remove rows with "No Rate" from data frame
IMDB <- subset(IMDB_noduplicates, Rate != "No Rate")
write.csv(IMDB, file="IMDB.csv")
```

Rate is till the type `r class(IMDB$Rate)` data. so lets convert it into float


```{r}
# Convert "Rate" column to float
IMDB$Rate <- as.numeric(IMDB$Rate)
```
Rate is now converted to `r class(IMDB$Rate)` data type.





```{r}

# Create a histogram of the Rate variable
hist(IMDB$Rate, 
     main = "Distribution of Movie Ratings", 
     xlab = "Rating", 
     ylab = "Frequency",
     breaks = 20,
     col = "#69b3a2",
     border = "white",
     xlim = c(0, 10),
     ylim = c(0, 1200),
     las = 1)

# Add a vertical line at the mean rating
abline(v = mean(IMDB$Rate), 
       col = "red", 
       lty = 2, 
       lwd = 2)

# Add a legend
legend("topright", 
       legend = c("Mean Rating"), 
       col = c("red"), 
       lty = c(2), 
       lwd = c(2), 
       bty = "n", 
       cex = 0.8)

```


```{r}
plot(IMDB[order(IMDB$Rate),]$Rate, 
     type = "l", # line plot
     col = "blue", # line color
     lwd = 2, # line width
     xlab = "Movie Index", # x-axis label
     ylab = "IMDB Rating", # y-axis label
     main = "IMDB Movie Ratings", # plot title
     ylim = c(0, 10)) # y-axis limits

# Add a grid
grid()

# Add a horizontal line at mean rating
abline(h = mean(IMDB$Rate), 
       col = "red", # line color
       lty = "dashed") # line style

# Add a legend
legend("topleft", 
       legend = c("IMDB Rating", "Mean Rating"), 
       col = c("blue", "red"), 
       lty = c(1, 2), 
       lwd = c(2, 1))
```



```{r}
summary(IMDB)

```
This is after removing the character data types which were with value "No Rate" in the data frame and also all the float values were as character type, so had to convert it to the float values.


### Cleaning and formatting the Votes variable

```{r}
head(IMDB$Votes)
```


```{r}
IMDB$Votes <- gsub(",","",IMDB$Votes)
head(IMDB$Votes)
class(IMDB$Votes)
```

 


```{r}
non_numeric_votes <- IMDB$Votes[!is.numeric(IMDB$Votes)]

# Get unique non-numeric values in "Votes"

```


```{r}
IMDB$Votes <- as.numeric(IMDB$Votes)
class(IMDB$Votes)
```

```{r}
hist(IMDB$Votes, 
     main = "Distribution of Movie Votings", 
     xlab = "Votes", 
     ylab = "Frequency",
     breaks = 20,
     col = "#69b3a2",
     border = "white"
     )

# Add a vertical line at the mean rating
abline(v = mean(IMDB$Votes), 
       col = "red", 
       lty = 2, 
       lwd = 2)

# Add a legend
legend("topright", 
       legend = c("Mean Rating"), 
       col = c("red"), 
       lty = c(2), 
       lwd = c(2), 
       bty = "n", 
       cex = 0.8)

```




```{r}
plot(IMDB[order(IMDB$Votes),]$Votes, 
     type = "l", # line plot
     col = "blue", # line color
     lwd = 2, # line width
     xlab = "Movie Index", # x-axis label
     ylab = "IMDB Voting", # y-axis label
     main = "IMDB Movie Votings" # plot title
     ) # y-axis limits

# Add a grid
grid()

# Add a vertical line at the mean rating
abline(h = mean(IMDB$Votes), 
       col = "red", # line color
       lty = "dashed") # line style

# Add a legend
legend("topleft", 
       legend = c("IMDB Voting", "Mean Voting"), 
       col = c("blue", "red"), 
       lty = c(1, 2), 
       lwd = c(2, 1))
```
The above code is manipulating and visualizing the "Votes" variable of the "IMDB" data frame, removing commas, converting to numeric, and plotting its distribution and a line plot.

### Cleaning and Formatting Duration variable
```{r, results='asis'}
non_numeric_Duration <- IMDB$Duration[!is.numeric(IMDB$Duration)]

# Get unique non-numeric values in "Duration"
unique(non_numeric_Duration)

# Remove rows with "None" from data frame
IMDB <- subset(IMDB, Duration != "None")
write.csv(IMDB, file="IMDB.csv")
class(IMDB$Duration)

IMDB$Duration <- as.integer(IMDB$Duration)

print(summary(IMDB))
```


```{r}

```


```{r}
hist(IMDB$Duration, 
     main = "Distribution of IMDB Duration", 
     xlab = "Duration", 
     ylab = "Frequency",
     breaks = 20,
     col = "#8F74FF",
     border = "white"
     )

# Add a vertical line at the mean rating
abline(v = mean(IMDB$Duration), 
       col = "red", 
       lty = 2, 
       lwd = 2)

# Add a legend
legend("topright", 
       legend = c("Mean Duration"), 
       col = c("red"), 
       lty = c(2), 
       lwd = c(2), 
       bty = "n", 
       cex = 0.8)

```

```{r}
plot(IMDB[order(IMDB$Duration),]$Duration, 
     type = "l", # line plot
     col = "#8F74FF", # line color
     lwd = 2, # line width
     xlab = "Movie Index", # x-axis label
     ylab = "Duration", # y-axis label
     main = "IMDB Duration") # plot title

# Add a grid
grid()

# Add a horizontal line at mean rating
abline(h = mean(IMDB$Duration), 
       col = "red", # line color
       lty = "dashed") # line style

# Add a legend
legend("topleft", 
       legend = c("IMDB Duration", "Mean Duration"), 
       col = c("#8F74FF", "red"), 
       lty = c(1, 2), 
       lwd = c(2, 1))
```
The above code first checks for non-numeric values in Duration variable, removes rows with "None" value, converts Duration variable from character to integer data type, prints summary statistics of the data frame, and then creates histograms and line plots to visualize the distribution of Duration variable.

### Cleaning and Formatting Genre variable
```{r}
head(IMDB$Genre)
```

```{r }
values <- unlist(strsplit(IMDB$Genre, ","))
unique(values)

```

```{r}
IMDB$Genre <- gsub(" ","",IMDB$Genre)
unique(unlist(strsplit(IMDB$Genre, ",")))
```

```{r}
library(highcharter)
library(tidyr)

df <- IMDB %>% separate_rows(Genre, sep = ",")

tidy_genres <- function(IMDB) {
  df %>%
    separate_rows(Genre, sep = ",")
}


g_df <- as.data.frame(table(df$Genre))
g_hc <- g_df  %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Genre Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )

  ghtml <-  hc_title(g_hc,text = "Genre Frequency in IMDB") %>%
            hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(ghtml, file = "ghtml.html")
ghtml
```
The above code reads in data about movies from IMDB, cleans and processes it to remove any missing or non-numeric values in the "Duration" column and split and clean the "Genre" column. It then creates visualizations of the cleaned data using highcharter library, including a histogram and line plot of the duration of movies, as well as a pie chart of the frequency of different movie genres in the dataset. The resulting plots and chart are saved as HTML files.










```{r}
IMDB$Episodes <- gsub("-","0",IMDB$Episodes)
head(IMDB$Episodes)
write.csv(IMDB, file="IMDB.csv")

class(IMDB$Episodes)
IMDB$Episodes <- as.numeric(IMDB$Episodes)
class(IMDB$Episodes)

summary(IMDB)
```


```{r}
summary(IMDB)

countn <- (IMDB[IMDB$Type == "Series" & IMDB$Duration > 200, ])
countn
IMDB$Duration <- ifelse(IMDB$Type == "Series" & IMDB$Duration > 200, IMDB$Duration/IMDB$Episodes, IMDB$Duration)

summary(IMDB)
```


```{r}
plot(IMDB[order(IMDB$Duration),]$Duration, 
     type = "l", # line plot
     col = "blue", # line color
     lwd = 2, # line width
     xlab = "Movie Index", # x-axis label
     ylab = "IMDB Duration", # y-axis label
     main = "IMDB Movie Duration" # plot title
     ) # y-axis limits

# Add a grid
grid()

abline(h = mean(IMDB$Duration), 
       col = "red", # line color
       lty = "dashed") # line style

# Add a legend
legend("topleft", 
       legend = c("IMDB Duration", "Mean Duration"), 
       col = c("blue", "red"), 
       lty = c(1, 2), 
       lwd = c(2, 1))
```
```{r}
summary(IMDB)
IMDB$Type <- as.factor(IMDB$Type)
summary(IMDB)
```


```{r, results='asis'}
library(highcharter)
Type_df <- as.data.frame(table(IMDB$Type))
Type_hc <- Type_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Type Movies or Series",
    dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  thtml <- hc_title(Type_hc,text = "Movies or Series Frequency in IMDB") %>%
           hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(thtml, file = "thtml.html")
thtml
```


```{r}
IMDB$Certificate <- as.factor(IMDB$Certificate)
```


```{r, results='asis'}
library(highcharter)
Certificate_df <- as.data.frame(table(IMDB$Certificate))
Certificate_hc <- Certificate_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Certificate",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  chtml <- hc_title(Certificate_hc,text = "Certificate Frequency in IMDB") %>%
           hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(chtml, file = "chtml.html")
chtml
```






```{r}
temp <- IMDB
head(temp)
head(IMDB)
```

```{r}
temp <- subset(temp, (Nudity == "No Rate" & Violence == "No Rate" & Profanity == "No Rate" & Alcohol == "No Rate" & Frightening == "No Rate"))
temp
write.csv(temp, file="temp.csv")
```

```{r}
IMDB <- subset(IMDB, !(Nudity == "No Rate" & Violence == "No Rate" & Profanity == "No Rate" & Alcohol == "No Rate" & Frightening == "No Rate"))

write.csv(IMDB, file="IMDB.csv")
```

```{r}
unique(IMDB$Nudity)
unique(IMDB$Violence)
unique(IMDB$Profanity)
unique(IMDB$Alcohol)
unique(IMDB$Frightening)


IMDB$Nudity <- gsub("No Rate","None",IMDB$Nudity)
IMDB$Violence <- gsub("No Rate","None",IMDB$Violence)
IMDB$Profanity <- gsub("No Rate","None",IMDB$Profanity)
IMDB$Alcohol <- gsub("No Rate","None",IMDB$Alcohol)
IMDB$Frightening <- gsub("No Rate","None",IMDB$Frightening)

unique(IMDB$Nudity)
unique(IMDB$Violence)
unique(IMDB$Profanity)
unique(IMDB$Alcohol)
unique(IMDB$Frightening)

write.csv(IMDB, file="IMDB.csv")
```


```{r}
unique(IMDB$Nudity)
unique(IMDB$Violence)
unique(IMDB$Profanity)
unique(IMDB$Alcohol)
unique(IMDB$Frightening)
unique(unlist(strsplit(IMDB$Genre, ",")))
unique(IMDB$Type)
unique(IMDB$Certificate)
```


```{r}
 IMDB$Nudity <- as.factor(IMDB$Nudity)
IMDB$Violence <- as.factor(IMDB$Violence)
IMDB$Profanity <- as.factor(IMDB$Profanity)
IMDB$Alcohol <- as.factor(IMDB$Alcohol)
IMDB$Frightening <- as.factor(IMDB$Frightening)

summary(IMDB)
```



```{r, results='asis'}
library(highcharter)
Nudity_df <- as.data.frame(table(IMDB$Nudity))
Nudity_hc <- Nudity_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Nudity Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  nhtml <- hc_title(Nudity_hc,text = "Nudity Frequency in IMDB") %>%
           hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(nhtml, file = "nhtml.html")
nhtml
```



```{r}
library(highcharter)
Violence_df <- as.data.frame(table(IMDB$Violence))
Violence_hc <- Violence_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Violence Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  vhtml <- hc_title(Violence_hc,text = "Violence Frequency in IMDB") %>%
           hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(vhtml, file = "vhtml.html")
vhtml
```


```{r}
library(highcharter)
Profanity_df <- as.data.frame(table(IMDB$Profanity))
Profanity_hc <- Profanity_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Profanity Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  phtml <-hc_title(Profanity_hc,text = "Profanity Frequency in IMDB") %>%
          hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(phtml, file = "phtml.html")
phtml
```


```{r}
library(highcharter)
Alcohol_df <- as.data.frame(table(IMDB$Alcohol))
Alcohol_hc <- Alcohol_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Alcohol Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  ahtml <-  hc_title(Alcohol_hc,text = "Alcohol Frequency in IMDB") %>%
            hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(ahtml, file = "ahtml.html")
ahtml
```

```{r}
library(highcharter)
Frightening_df <- as.data.frame(table(IMDB$Frightening))
Frightening_hc <- Frightening_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Frightening Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  fhtml <-  hc_title(Frightening_hc,text = "Frightening Frequency in IMDB") %>%
            hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(fhtml, file = "fhtml.html")
fhtml
```

```{r}
summary(IMDB)
```



```{r}
head(IMDB)
```




```{r}
write.csv(IMDB, file="IMDB.csv")
```



