---
title: "DECODING IMDb POPULARITY - Mid Term Summary Paper"
author: "Team SIM"
date: "2023-03-02"
output:
  rmdformats::readthedown:
    code_folding: hide
---

<style>
p{ /* Normal  */
   font-size: 18px;
}

body{ /* Normal  */
   font-size: 18px;
}
td {  /* Table  */
   font-size: 14px;
}
h1 { /* Header 1 */
 font-size: 32px;
 color: #deb522;
}
h2 { /* Header 2 */
 font-size: 26px;
 color: #deb522;
}
h3 { /* Header 3 */
 font-size: 22px;
 color: #deb522;
}
code.r{ /* Code block */
  font-size: 14px;
}
pre { /* Code block */
  font-size: 14px
}
</style>



```{r init, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
knitr::opts_chunk$set(warning = F, results = "markup", message = F, comment = NA)
# knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```


# Section I: Introduction

## 1.1: Background on IMDb.

IMDb, which stands for the Internet Movie Database, is an online database of information related to movies, television shows, and video games. It was founded in 1990 by Col Needham and has since become one of the most popular websites for movie and television enthusiasts. The website provides a vast array of information, including plot summaries, cast and crew information, trivia, user ratings and reviews, and box office performance data.

IMDb is owned by Amazon, and it has become an important resource for both fans and industry professionals alike. Many actors, directors, and writers use IMDb as a platform to showcase their work, while fans use it to discover new movies and shows with a good rating to watch. Additionally, IMDb is frequently used by the studios and production companies to research potential hires and track the performance of their films and television shows.

## 1.2: Project Motivation

Understanding the factors that contribute to a movie or TV show's popularity on IMDb is an important topic for both fans and industry professionals alike. For fans, knowing which movies and TV shows are popular on IMDb can help them discover new content to watch and inform their viewing choices. For industry professionals, understanding the factors that contribute to a movie or TV show's popularity on IMDb can help them make informed decisions about which projects to invest in and how to market and to also promote them.

By analyzing the IMDb database, we can gain insights into which factors are most strongly associated with a movie or TV show's popularity on the platform. This information can help both fans and industry professionals make more informed decisions about which movies and TV shows to watch and invest in, respectively. Additionally, understanding these factors can help inform the development of new movies and TV shows that are more likely to be popular on IMDb. Overall, the motivation for this project is to gain a deeper understanding of the factors that contribute to a movie or TV show's popularity on IMDb and how they differ between movies and TV shows.









```{r}
library(rmdformats)
library(ezids)
library(highcharter)
library(tidyr)
library(ggplot2)
library(plotly)
library(ggcorrplot)
library(dplyr)
library(stats)
```


# Data Cleaning and Formating

## Reading the RAW CSV file 
```{r}
#Reading the Raw CSV of IMDB Data Frame
IMDB_raw <- read.csv("imdb_SIM_raw.csv",header = TRUE)
summary(IMDB_raw)
```




### Removing the Duplicates
```{r}
# Removing all the duplicate data from the df IMDB
IMDB_noduplicates <- distinct(IMDB_raw, Name, .keep_all = TRUE)
write.csv(IMDB_noduplicates, "IMDB_noduplicates.csv")
```


### Storing the removed duplicates into new CSV file
```{r}
# the duplicated rows that are removed are just stored into a New CSV file just for reference and presentation
dup_idx <- duplicated(IMDB_raw)
dup_rows <- IMDB_raw[dup_idx, ]
write.csv(dup_rows,"IMDB_duplicate_rows.csv")
```
### Calculating the number of missing values
```{r}
sum(is.na(IMDB_noduplicates))
```
### Returning the dimensions (number of rows and columns) of the dataset 
```{r}
dim(IMDB_noduplicates)
```

### Returning the first six rows of the dataset 
```{r}
head(IMDB_noduplicates)
```

### Structure of dataset
```{r}
str(IMDB_noduplicates)
```

###  Summarizing the statistical properties of the variables (no duplicates) in the dataset
```{r}
summary(IMDB_noduplicates)
```

### Cleaning and formatting the Rate variable

Rate Variable must be Numeric.Let's Check if "Rate" is Numeric or not `r is.numeric(IMDB_noduplicates$Rate)`

```{r}
# Pulling out the list of non numeric or float values in the "Rate" Variable
non_float_rate <- IMDB_noduplicates$Rate[!is.double(IMDB_noduplicates$Rate)]

# Get unique non-float values in "Rate"
print(unique(non_float_rate))
```
```{r}

# we see that first row data of Rate is numeric. But lets see how R is reading the same.
class(IMDB_noduplicates$Rate[1])
```
Now that we know from Rate variable it had both float and character data types but R is understanding that other float values are also characters. so lets do two things (1) Removing all the rows with "No Rate" data in IMDB data frame.
                                  (2) Check and convert the Rate variable to float

```{r}
# Remove rows with "No Rate" from data frame
IMDB <- subset(IMDB_noduplicates, Rate != "No Rate")
write.csv(IMDB, file="IMDB.csv")
```

Rate is till the type `r class(IMDB$Rate)` data. so lets convert it into float


```{r}
# Convert "Rate" column to float
IMDB$Rate <- as.numeric(IMDB$Rate)
```
Rate is now converted to `r class(IMDB$Rate)` data type.





```{r}

# Create a histogram of the Rate variable
hist(IMDB$Rate, 
     main = "Distribution of Movie Ratings", 
     xlab = "Rating", 
     ylab = "Frequency",
     breaks = 20,
     col = "#69b3a2",
     border = "white",
     xlim = c(0, 10),
     ylim = c(0, 1200),
     las = 1)

# Add a vertical line at the mean rating
abline(v = mean(IMDB$Rate), 
       col = "red", 
       lty = 2, 
       lwd = 2)

# Add a legend
legend("topright", 
       legend = c("Mean Rating"), 
       col = c("red"), 
       lty = c(2), 
       lwd = c(2), 
       bty = "n", 
       cex = 0.8)

```


```{r}
plot(IMDB[order(IMDB$Rate),]$Rate, 
     type = "l", # line plot
     col = "blue", # line color
     lwd = 2, # line width
     xlab = "Movie Index", # x-axis label
     ylab = "IMDB Rating", # y-axis label
     main = "IMDB Movie Ratings", # plot title
     ylim = c(0, 10)) # y-axis limits

# Add a grid
grid()

# Add a horizontal line at mean rating
abline(h = mean(IMDB$Rate), 
       col = "red", # line color
       lty = "dashed") # line style

# Add a legend
legend("topleft", 
       legend = c("IMDB Rating", "Mean Rating"), 
       col = c("blue", "red"), 
       lty = c(1, 2), 
       lwd = c(2, 1))
```



```{r}
summary(IMDB)

```
This is after removing the character data types which were with value "No Rate" in the data frame and also all the float values were as character type, so had to convert it to the float values.


### Cleaning and formatting the Votes variable

```{r}
head(IMDB$Votes)
```


```{r}
IMDB$Votes <- gsub(",","",IMDB$Votes)
head(IMDB$Votes)
class(IMDB$Votes)
```

 


```{r}
non_numeric_votes <- IMDB$Votes[!is.numeric(IMDB$Votes)]

# Get unique non-numeric values in "Votes"

```


```{r}
IMDB$Votes <- as.numeric(IMDB$Votes)
class(IMDB$Votes)
```

```{r}
hist(IMDB$Votes, 
     main = "Distribution of Movie Votings", 
     xlab = "Votes", 
     ylab = "Frequency",
     breaks = 20,
     col = "#69b3a2",
     border = "white"
     )

# Add a vertical line at the mean rating
abline(v = mean(IMDB$Votes), 
       col = "red", 
       lty = 2, 
       lwd = 2)

# Add a legend
legend("topright", 
       legend = c("Mean Rating"), 
       col = c("red"), 
       lty = c(2), 
       lwd = c(2), 
       bty = "n", 
       cex = 0.8)

```




```{r}
plot(IMDB[order(IMDB$Votes),]$Votes, 
     type = "l", # line plot
     col = "blue", # line color
     lwd = 2, # line width
     xlab = "Movie Index", # x-axis label
     ylab = "IMDB Voting", # y-axis label
     main = "IMDB Movie Votings" # plot title
     ) # y-axis limits

# Add a grid
grid()

# Add a vertical line at the mean rating
abline(h = mean(IMDB$Votes), 
       col = "red", # line color
       lty = "dashed") # line style

# Add a legend
legend("topleft", 
       legend = c("IMDB Voting", "Mean Voting"), 
       col = c("blue", "red"), 
       lty = c(1, 2), 
       lwd = c(2, 1))
```
The above code is manipulating and visualizing the "Votes" variable of the "IMDB" data frame, removing commas, converting to numeric, and plotting its distribution and a line plot.

### Cleaning and Formatting Duration variable
```{r, results='asis'}
non_numeric_Duration <- IMDB$Duration[!is.numeric(IMDB$Duration)]

# Get unique non-numeric values in "Duration"
unique(non_numeric_Duration)

# Remove rows with "None" from data frame
IMDB <- subset(IMDB, Duration != "None")
write.csv(IMDB, file="IMDB.csv")
class(IMDB$Duration)

IMDB$Duration <- as.integer(IMDB$Duration)

print(summary(IMDB))
```


```{r}

```


```{r}
hist(IMDB$Duration, 
     main = "Distribution of IMDB Duration", 
     xlab = "Duration", 
     ylab = "Frequency",
     breaks = 20,
     col = "#8F74FF",
     border = "white"
     )

# Add a vertical line at the mean rating
abline(v = mean(IMDB$Duration), 
       col = "red", 
       lty = 2, 
       lwd = 2)

# Add a legend
legend("topright", 
       legend = c("Mean Duration"), 
       col = c("red"), 
       lty = c(2), 
       lwd = c(2), 
       bty = "n", 
       cex = 0.8)

```

```{r}
plot(IMDB[order(IMDB$Duration),]$Duration, 
     type = "l", # line plot
     col = "#8F74FF", # line color
     lwd = 2, # line width
     xlab = "Movie Index", # x-axis label
     ylab = "Duration", # y-axis label
     main = "IMDB Duration") # plot title

# Add a grid
grid()

# Add a horizontal line at mean rating
abline(h = mean(IMDB$Duration), 
       col = "red", # line color
       lty = "dashed") # line style

# Add a legend
legend("topleft", 
       legend = c("IMDB Duration", "Mean Duration"), 
       col = c("#8F74FF", "red"), 
       lty = c(1, 2), 
       lwd = c(2, 1))
```
The above code first checks for non-numeric values in Duration variable, removes rows with "None" value, converts Duration variable from character to integer data type, prints summary statistics of the data frame, and then creates histograms and line plots to visualize the distribution of Duration variable.

### Cleaning and Formatting Genre variable
```{r}
head(IMDB$Genre)
```

```{r }
values <- unlist(strsplit(IMDB$Genre, ","))
unique(values)

```

```{r}
IMDB$Genre <- gsub(" ","",IMDB$Genre)
unique(unlist(strsplit(IMDB$Genre, ",")))
```

```{r}


df <- IMDB %>% separate_rows(Genre, sep = ",")

tidy_genres <- function(IMDB) {
  df %>%
    separate_rows(Genre, sep = ",")
}


g_df <- as.data.frame(table(df$Genre))
g_hc <- g_df  %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Genre Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )

  ghtml <-  hc_title(g_hc,text = "Genre Frequency in IMDB") %>%
            hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(ghtml, file = "ghtml.html")
ghtml
```
The above code reads in data about movies from IMDB, cleans and processes it to remove any missing or non-numeric values in the "Duration" column and split and clean the "Genre" column. It then creates visualizations of the cleaned data using highcharter library, including a histogram and line plot of the duration of movies, as well as a pie chart of the frequency of different movie genres in the dataset. The resulting plots and chart are saved as HTML files.










```{r}
IMDB$Episodes <- gsub("-","0",IMDB$Episodes)
head(IMDB$Episodes)
write.csv(IMDB, file="IMDB.csv")

class(IMDB$Episodes)
IMDB$Episodes <- as.numeric(IMDB$Episodes)
class(IMDB$Episodes)

summary(IMDB)
```
The above code replaces any hyphens in the "Episodes" column of the IMDB dataset with zeros, converts the column to numeric format, and saves the updated dataset as a CSV file.


```{r}
summary(IMDB)

countn <- (IMDB[IMDB$Type == "Series" & IMDB$Duration > 200, ])
countn
IMDB$Duration <- ifelse(IMDB$Type == "Series" & IMDB$Duration > 200, IMDB$Duration/IMDB$Episodes, IMDB$Duration)

summary(IMDB)
```
The above code first replaces any hyphens in the "Episodes" column with zeros, and then converts it to a numeric data type.
Next, it filters rows in the "IMDB" dataframe where the "Type" column is "Series" and the "Duration" column is greater than 200, and stores the resulting dataframe in "countn".
Then, for rows where "Type" is "Series" and "Duration" is greater than 200, it divides the "Duration" column by the "Episodes" column, otherwise it leaves it unchanged. Finally, it prints a summary of the "IMDB" dataframe.

```{r}
plot(IMDB[order(IMDB$Duration),]$Duration, 
     type = "l", # line plot
     col = "blue", # line color
     lwd = 2, # line width
     xlab = "Movie Index", # x-axis label
     ylab = "IMDB Duration", # y-axis label
     main = "IMDB Movie Duration" # plot title
     ) # y-axis limits

# Add a grid
grid()

abline(h = mean(IMDB$Duration), 
       col = "red", # line color
       lty = "dashed") # line style

# Add a legend
legend("topleft", 
       legend = c("IMDB Duration", "Mean Duration"), 
       col = c("blue", "red"), 
       lty = c(1, 2), 
       lwd = c(2, 1))
```
The above code creates a line plot of IMDB movie duration with a horizontal dashed line indicating the mean duration, and adds a legend.
### Converting and Summarizing IMDB Data and Changing Type Column to Factor
```{r}
summary(IMDB)
IMDB$Type <- as.factor(IMDB$Type)
summary(IMDB)
```


```{r, results='asis'}
Type_df <- as.data.frame(table(IMDB$Type))
Type_hc <- Type_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Type Movies or Series",
    dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  thtml <- hc_title(Type_hc,text = "Movies or Series Frequency in IMDB") %>%
           hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(thtml, file = "thtml.html")
thtml
```
The above code generates a pie chart using the highcharter package to visualize the frequency of movie and series types in the IMDB dataset. The chart is then saved as an HTML file and displayed in the output using htmlwidgets::saveWidget and thtml.

```{r}
IMDB$Certificate <- as.factor(IMDB$Certificate)
```


```{r, results='asis'}
Certificate_df <- as.data.frame(table(IMDB$Certificate))
Certificate_hc <- Certificate_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Certificate",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  chtml <- hc_title(Certificate_hc,text = "Certificate Frequency in IMDB") %>%
           hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(chtml, file = "chtml.html")
chtml
```
The above code generates a pie chart showing the frequency of different certificate ratings in the IMDB dataset. It first converts the "Certificate" column to a factor, then creates a data frame with the frequency of each certificate using the "table" function. Finally, it uses the "hchart" function from the "highcharter" package to create a pie chart with data labels and a title. The resulting chart is saved as an interactive HTML file.





```{r}
temp <- IMDB
head(temp)
head(IMDB)
```
### Filtering the temp dataframe to include only rows 
```{r}
temp <- subset(temp, (Nudity == "No Rate" & Violence == "No Rate" & Profanity == "No Rate" & Alcohol == "No Rate" & Frightening == "No Rate"))
write.csv(temp, file="temp.csv")
```

```{r}
IMDB <- subset(IMDB, !(Nudity == "No Rate" & Violence == "No Rate" & Profanity == "No Rate" & Alcohol == "No Rate" & Frightening == "No Rate"))

write.csv(IMDB, file="IMDB.csv")
```
The above code removes all rows from the IMDB dataframe where all five variables Nudity, Violence, Profanity, Alcohol, and Frightening have the value "No Rate"

```{r}
unique(IMDB$Nudity)
unique(IMDB$Violence)
unique(IMDB$Profanity)
unique(IMDB$Alcohol)
unique(IMDB$Frightening)


IMDB$Nudity <- gsub("No Rate","None",IMDB$Nudity)
IMDB$Violence <- gsub("No Rate","None",IMDB$Violence)
IMDB$Profanity <- gsub("No Rate","None",IMDB$Profanity)
IMDB$Alcohol <- gsub("No Rate","None",IMDB$Alcohol)
IMDB$Frightening <- gsub("No Rate","None",IMDB$Frightening)

unique(IMDB$Nudity)
unique(IMDB$Violence)
unique(IMDB$Profanity)
unique(IMDB$Alcohol)
unique(IMDB$Frightening)

write.csv(IMDB, file="IMDB.csv")
```
The above code replaces all instances of "No Rate" in the Nudity, Violence, Profanity, Alcohol, and Frightening columns with "None" and then saves the updated data as a CSV file named "IMDB.csv". It also prints the unique values in each of the columns before and after the replacement.

### Extracting Unique Values from Multiple Columns in IMDB Dataset
```{r}
unique(IMDB$Nudity)
unique(IMDB$Violence)
unique(IMDB$Profanity)
unique(IMDB$Alcohol)
unique(IMDB$Frightening)
unique(unlist(strsplit(IMDB$Genre, ",")))
unique(IMDB$Type)
unique(IMDB$Certificate)
```

### Converting columns in IMDB dataset to factors.
```{r}
 IMDB$Nudity <- as.factor(IMDB$Nudity)
IMDB$Violence <- as.factor(IMDB$Violence)
IMDB$Profanity <- as.factor(IMDB$Profanity)
IMDB$Alcohol <- as.factor(IMDB$Alcohol)
IMDB$Frightening <- as.factor(IMDB$Frightening)

summary(IMDB)
```



```{r, results='asis'}
Nudity_df <- as.data.frame(table(IMDB$Nudity))
Nudity_hc <- Nudity_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Nudity Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  nhtml <- hc_title(Nudity_hc,text = "Nudity Frequency in IMDB") %>%
           hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(nhtml, file = "nhtml.html")
nhtml
```
The above code creates a pie chart using highcharter package to display the frequency of Nudity in movies or series in IMDB dataset.

### Pie chart showing the frequency of violent content in movies and series on IMDB.
```{r}
Violence_df <- as.data.frame(table(IMDB$Violence))
Violence_hc <- Violence_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Violence Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  vhtml <- hc_title(Violence_hc,text = "Violence Frequency in IMDB") %>%
           hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(vhtml, file = "vhtml.html")
vhtml
```

### Code for creating a pie chart showing the frequency of profanity in movies and series in the IMDB dataset.
```{r}

Profanity_df <- as.data.frame(table(IMDB$Profanity))
Profanity_hc <- Profanity_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Profanity Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  phtml <-hc_title(Profanity_hc,text = "Profanity Frequency in IMDB") %>%
          hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(phtml, file = "phtml.html")
phtml
```

### Visualization of Alcohol Frequency in IMDB Movies and TV Series as a Pie Chart.
```{r}
Alcohol_df <- as.data.frame(table(IMDB$Alcohol))
Alcohol_hc <- Alcohol_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Alcohol Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  ahtml <-  hc_title(Alcohol_hc,text = "Alcohol Frequency in IMDB") %>%
            hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(ahtml, file = "ahtml.html")
ahtml
```
### Generating a pie chart to show the frequency of "frightening" content in movies and series listed on IMDB.
```{r}

Frightening_df <- as.data.frame(table(IMDB$Frightening))
Frightening_hc <- Frightening_df %>%
  hchart(
    "pie", hcaes(x = Var1, y = Freq),
    name = "Frightening Movies or Series",
        dataLabels = list(enabled = TRUE, format='{point.name}: {point.y} ({point.percentage:.1f}%)')

    )
  fhtml <-  hc_title(Frightening_hc,text = "Frightening Frequency in IMDB") %>%
            hc_subtitle(text = "Pie Chart")
htmlwidgets::saveWidget(fhtml, file = "fhtml.html")
fhtml
```

```{r}
summary(IMDB)
```
Now, it gives the data that has been cleaned and formatted.


```{r}
head(IMDB)
```
Viewing the first few rows of a data frame that is been cleaned and formatted




```{r}
write.csv(IMDB, file="IMDB.csv")
```
Writing the contents of the IMDB data frame to a CSV file named "IMDB.csv" in the current working directory so that we could read the CSV file while doing Exploratory Data Analysis.





## Exploratory Data Analysis




## Reading CSV file:
```{r}
IMDB <- read.csv("IMDB.csv")
```
Result : Reads and Assigns the data to a variable called IMDB.


### Histogram and Density plot - Distribution of Rate:
```{r}
# for IMDB whole
# Calculate summary statistics
mean_Rate <- mean(IMDB$Rate)
median_Rate <- median(IMDB$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```


Result : Understanding distribution of rate by calculating summary statistics using Histogram and Density plot.

### Subsets:
```{r}
IMDB_Film <- subset(IMDB,IMDB$Type=="Film")
head(IMDB_Film)

IMDB_Series <- subset(IMDB,IMDB$Type == "Series")
head(IMDB_Series)
```


Result : Creating two subsets of IMDB, i.e: IMDB_Film & IMDB_Series.


### For Movies:
```{r}
#  for movies
# Calculate summary statistics
mean_Rate <- mean(IMDB_Film$Rate)
median_Rate <- median(IMDB_Film$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB_Film$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB_Film$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB_Film, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB_Film") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB_Film, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB_Film") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```


Result : Calculated the summary statistics and plotted the distribution of rate using histogram and density plot.



### For Series:
```{r}
# for series

# Calculate summary statistics
mean_Rate <- mean(IMDB_Series$Rate)
median_Rate <- median(IMDB_Series$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB_Series$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB_Series$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB_Series, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB_Series") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB_Series, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB_Series") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```


Result : Calculated the summary statistics and plotted the distribution of rate using histogram and density plot.

### For both Film & Series:
```{r}
# Plot films and series on the same scatter plot
PVR <- ggplot() +
  # Films
  geom_point(data = IMDB_Film, aes(x = Votes, y = Rate, color = "Film"), size = 0.5) +
  # TV Series
  geom_point(data = IMDB_Series, aes(x = Votes, y = Rate, color = "TV Series"), size = 0.5) +
  # Add x and y axis labels
  labs(x = "Votes", y = "IMDB Rating") +
  # Add title
  ggtitle("IMDB Rating vs Votes for Films and TV Series") +
  # Add legend
  scale_color_manual(name = "Type", values = c("Film" = "#A90500", "TV Series" = "#0012A9"))

ggplotly(PVR)

```


Result : Plotted both film & Series using Scatter plot.




### For Genre:
```{r}
df <- IMDB %>% separate_rows(Genre, sep = ",")

tidy_genres <- function(IMDB) {
  df %>%
    separate_rows(Genre, sep = ",")
}

# getting the average rating for each genre
df_avg <- df %>%
  tidy_genres() %>%
  group_by(Genre) %>%
  summarise(avg_rating = mean(Rate))

# creating a bar plot with different colors for each genre
PGRA <- df_avg %>%
  ggplot(aes(x = Genre, y = avg_rating, fill = Genre)) +
  geom_col() +
  scale_fill_hue(name = "Genre") +
  labs(title = "Average Rating by Genre",
       x = "Genre",
       y = "Average Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplotly(PGRA)

```


Result : Average rating and bar plot was calculated for each genre.

### Colours for Each Genre:
```{r}

df_tidy <- df %>%
  tidy_genres()

genre_colors <- c("Action" = "#FFA500", "Adventure" = "#FFC0CB", "Thriller" = "#FFD700",
                  "Crime" = "#00FFFF", "Drama" = "#4169E1", "Sci-Fi" = "#9400D3",
                  "Comedy" = "#32CD32", "Sport" = "#FF69B4", "Horror" = "#FF4500",
                  "Mystery" = "#8B008B")


# create the box plot
PGR <- ggplot(df_tidy, aes(x = Genre, y = Rate)) +
  geom_boxplot() +
  scale_fill_manual(values = genre_colors) +
  labs(title = "Distribution of Ratings by Genre",
       x = "Genre",
       y = "Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplotly(PGR)


```


Result : Colours are assigned to each of the genre to under the analysis results better.

### Box plot for Genre:
```{r}
genre_colors <- c("Action" = "#FFA500", "Adventure" = "#FFC0CB", "Thriller" = "#FFD700",
                  "Crime" = "#00FFFF", "Drama" = "#4169E1", "Sci-Fi" = "#9400D3",
                  "Comedy" = "#32CD32", "Sport" = "#FF69B4", "Horror" = "#FF4500",
                  "Mystery" = "#8B008B")

# create box plot
ggplot(data = IMDB, aes(x = Certificate, y = Rate)) +
  geom_boxplot() +
  scale_fill_manual(values = genre_colors)+
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Certificate",
       x = "Certificate",
       y = "IMDB Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```


Result : Plotted a Box plot to understand the analysis on genre better.


```{r}
PTR <- ggplot(data = IMDB, aes(x = Type, y = Rate, fill = Type)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Type",
       x = "Type",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9"))
ggplotly(PTR)
```


Result : Plotted a box plot to understand the distribution of ratings by type.

### Duration and IMDB rating:

```{r}
# create scatter plot
p <- ggplot(data = IMDB, aes(x = Duration, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Duration",
       x = "Duration (minutes)",
       y = "IMDB Rating")

# convert ggplot to plotly object
ggplotly(p)

```


Result : Plotted a scatter plot with a regression line to understand the relationship between IMDB rating and duration.


### IMDB Rating and votes:
```{r}
# create scatter plot
p <- ggplot(data = IMDB, aes(x = Votes, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB  Rating vs. Votes",
       x = "Votes",
       y = "IMDB Rating")

# convert ggplot to plotly object
ggplotly(p)

```


Result : Plotted a scatter plot with a regression line to understand the relationship between IMDB rating and votes.

### IMDB Series rating and Episodes:
```{r}
# create scatter plot
p <- ggplot(data = IMDB_Series, aes(x = Episodes, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB Series Rating vs. Episodes",
       x = "Episodes",
       y = "IMDB Series Rating")

# convert ggplot to plotly object
ggplotly(p)

```


Result : Plotted a scatter plot with a regression line to understand the relationship between IMDB series rating and episodes.




### IMDB rating and content rating:
```{r}
# create scatter plot
ggplot(data = IMDB, aes(x = Rate, y = Nudity)) +
  geom_point(aes(color = "Nudity")) +
  
  # add other scatter plots
  geom_point(aes(x = Rate, y = Violence, color = "Violence")) +
  geom_point(aes(x = Rate, y = Profanity, color = "Profanity")) +
  geom_point(aes(x = Rate, y = Alcohol, color = "Alcohol")) +
  geom_point(aes(x = Rate, y = Frightening, color = "Frightening")) +
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Content Ratings",
       x = "IMDB Rating",
       y = "Content Rating") +
  
  # add legend
  scale_color_manual(name = "Content Rating",
                     values = c(Nudity = "red",
                                Violence = "blue",
                                Profanity = "green",
                                Alcohol = "purple",
                                Frightening = "orange"))

```


Result : Plotted a scatter plot to understand the relationship between IMDB rating and content ratings.







### Correlation heat map:
```{r}
# Select relevant numeric variables for correlation matrix
numeric_vars <- IMDB %>% 
  select_if(is.numeric)
# Compute the correlation matrix
cor_matrix <- cor(numeric_vars)

# Create the heatmap using ggcorrplot
ggcorrplot(cor_matrix, type = "lower", hc.order = TRUE, lab = TRUE)

```


Results : Computed the correlation matrix and created a heat map using ggcorrplot.

### Ratings and the Characteristics of Film & Series:
```{r}
PRN <- ggplot(data = IMDB, aes(x = Nudity, y = Rate, fill = Nudity)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Nudity",
       x = "Nudity",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRN)


PRV <- ggplot(data = IMDB, aes(x = Violence, y = Rate, fill = Violence)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Violence",
       x = "Violence",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRV)


PRP <- ggplot(data = IMDB, aes(x = Profanity, y = Rate, fill = Profanity)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Profanity",
       x = "Profanity",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRP)


PRA <- ggplot(data = IMDB, aes(x = Alcohol, y = Rate, fill = Alcohol)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Alcohol",
       x = "Alcohol",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRA)


PRF <- ggplot(data = IMDB, aes(x = Frightening, y = Rate, fill = Frightening)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Frightening",
       x = "Frightening",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRF)

```


Results : Plotted the Box plot to understand the Distribution of Rating by nudity, violence, profanity, alcohol, frightening.















#### Analysis of Variance


### Anova for Content variables with both Film and Series

```{r}
aov_model <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB)

aov_output <- summary(aov_model)

print(aov_output)
```

The variables of Violence, Profanity, Alcohol, and Frightening have a significant difference between them, while the Nudity variable does not have a significant difference. This table provides valuable insights into the differences between the variables in the dataset.



### Anova for Content variables with Film

```{r}
aov_model_film <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB_Film)

aov_film_output <- summary(aov_model_film)

print(aov_film_output)
```
From the table, we can see that all of the variables have a significant difference between them, with Alcohol and Frightening having the highest F-values and the lowest p-values, indicating that the difference between their average values is the most significant.

The Nudity, Violence, and Profanity variables also have a significant difference, but not as significant as Alcohol and Frightening.


### Anova for Content variables with Series


```{r}
aov_model_series <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB_Series)

aov_series_output <- summary(aov_model_series)

print(aov_series_output)
```
From the table, we can see that all of the variables have a significant difference between them, with Violence having the highest F-value and the lowest p-value, indicating that the difference between its average value and the others is the most significant.

The other variables of Nudity, Profanity, Alcohol, and Frightening also have a significant difference, but not as significant as Violence.


### Anova for Nudity with Both (Film and series), Film & Series 
```{r}
summary(aov(Rate~Nudity,data=IMDB))
summary(aov(Rate~Nudity,data=IMDB_Film))
summary(aov(Rate~Nudity,data=IMDB_Series))
```
Film and Series : From the table, we can see that there is no significant difference between the average values of Nudity in the dataset. This is because the p-value is higher than the commonly used alpha level of 0.05.

Film : From the table, we can see that the p-value is less than the commonly used alpha level of 0.05, which indicates that there is a significant difference between the average values of Nudity in the dataset. The asterisks (**), next to the p-value, indicate the level of significance; in this case, two asterisks indicate a p-value less than 0.01.

Series: From the table, we can see that the p-value is less than the commonly used alpha level of 0.05, which indicates that there is a significant difference between the average values of Nudity in the dataset.The asterisk (*) next to the p-value indicates the level of significance, where a single asterisk indicates a p-value less than 0.05.



### Anova for Violence with Both (Film and series), Film & Series 


```{r}
summary(aov(Rate~Violence,data=IMDB))
summary(aov(Rate~Violence,data=IMDB_Film))
summary(aov(Rate~Violence,data=IMDB_Series))
```
Film and Series : In this case, the variable "Violence" has a significant effect on the outcome variable, as the p-value is less than 0.05 (indicated by "*"). Therefore, we reject the null hypothesis that the variable "Violence" has no effect on the outcome variable.

Film : The table indicates that there is a significant difference between groups (p < 0.01), meaning that the "Violence" variable varies significantly depending on Rate

Series : The results indicate that there is a significant effect of "Violence" on "Rate", as evidenced by the very small p-value (7.4e-06) and the significant F value (8.95). Therefore, we can conclude that "Violence" has a significant impact on the ratings of TV series in this dataset.

For the variable Violence, there is a statistically significant effect on Rate in all three datasets (p < 0.01), indicating that the amount of violence in a movie or TV show is related to the audience's rating of it.


```{r}
summary(aov(Rate~Profanity,data=IMDB))
summary(aov(Rate~Profanity,data=IMDB_Film))
summary(aov(Rate~Profanity,data=IMDB_Series))
```

These are the ANOVA results for the relationship between "Rate" and "Profanity" in the "IMDB", "IMDB_Film", and "IMDB_Series" datasets. In all three datasets, the "Profanity" variable is significant at the p < .01 level, indicating a significant relationship between the amount of profanity in a movie or series and its rating.

```{r}
summary(aov(Rate~Alcohol,data=IMDB))
summary(aov(Rate~Alcohol,data=IMDB_Film))
summary(aov(Rate~Alcohol,data=IMDB_Series))
```
For the variable Alcohol, there is a statistically significant effect on Rate in all three datasets (p < 0.01), indicating that the portrayal of alcohol in movies and TV shows affects how the audience rates them.

```{r}
summary(aov(Rate~Frightening,data=IMDB))
summary(aov(Rate~Frightening,data=IMDB_Film))
summary(aov(Rate~Frightening,data=IMDB_Series))
```







## Liner Regression Model
### LM model for Rate and Duration in Film and Series

```{r}
lm_model <- lm(Rate ~ Duration , data = IMDB)

# Get the summary of the regression model
print(summary(lm_model))
```


The intercept is 7.419, which represents the estimated mean rating when the duration is zero. The coefficient for 'Duration' is -0.004764, which indicates that the estimated mean rating decreases by 0.004764 for every additional minute of duration.

The p-value for the coefficient of 'Duration' is less than 2e-16, which indicates that the relationship between 'Duration' and 'Rate' is statistically significant. The R-squared value is 0.028, which indicates that only 2.8% of the variability in 'Rate' can be explained by 'Duration'.

The F-statistic is significant with a p-value of less than 2e-16, which confirms that the model is a good fit for the data. The residual standard error is 1.02, which indicates the average difference between the observed 'Rate' and the predicted 'Rate' values is 1.02 units.











### LM model for Rate and Votes in Film and Series


```{r}
lm_model <- lm(Rate ~ Votes, data = IMDB)

# Get the summary of the regression model
summary(lm_model)
```
The regression model for Rate and Votes shows that the p-value for the regression coefficient is less than 0.05, indicating that there is a statistically significant relationship between the two variables. The coefficient estimate for Votes is 1.49e-06, indicating that for every additional vote, the rate increases by approximately 1.49e-06 units. The adjusted R-squared value is 0.0989, indicating that only 9.89% of the variation in Rate is explained by the variation in Votes. Overall, while there is a statistically significant relationship between the two variables, Votes alone does not explain much of the variation in Rate.


### LM model for Rate and Episodes in Series



```{r}
summary(lm(Rate ~ Episodes, data = IMDB_Series))
```



This is a simple linear regression model with one predictor variable, Episodes, and one response variable, Rate. The coefficient for Episodes is -2.62e-04, indicating that for each additional episode, the predicted Rate score decreases by approximately 0.00026. The intercept is 7.70e+00, indicating that if a series had zero episodes, the predicted Rate score would be 7.70.

The p-value for the coefficient of Episodes is less than 0.05, suggesting that the relationship between Episodes and Rate is statistically significant. The R-squared value is 0.075, indicating that the model explains only a small proportion of the variation in the data. The residual standard error is 0.812, indicating that the model's predictions are typically off by about 0.81 on the Rate scale.






