---
title: "EDA"
author: "TEAM SIM"
date: "2023-03-23"
output: html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r init, include=TRUE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='asis',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "asis", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

## Reading CSV file:
```{r}
IMDB <- read.csv("IMDB.csv")
```
Result : Reads and Assigns the data to a variable called IMDB.


## Histogram and Density plot - Distribution of Rate:
```{r}
# for IMDB whole
# Calculate summary statistics
mean_Rate <- mean(IMDB$Rate)
median_Rate <- median(IMDB$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```
Result : Understanding distribution of rate by calculating summary statistics using Histogram and Density plot.

## Subsets:
```{r}
IMDB_Film <- subset(IMDB,IMDB$Type=="Film")
head(IMDB_Film)

IMDB_Series <- subset(IMDB,IMDB$Type == "Series")
head(IMDB_Series)
```
Result : Creating two subsets of IMDB, i.e: IMDB_Film & IMDB_Series.


## For Movies:
```{r}
#  for movies
# Calculate summary statistics
mean_Rate <- mean(IMDB_Film$Rate)
median_Rate <- median(IMDB_Film$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB_Film$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB_Film$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB_Film, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB_Film") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB_Film, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB_Film") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```
Result : Calculated the summary statistics and plotted the distribution of rate using histogram and density plot.



## For Series:
```{r}
# for series

# Calculate summary statistics
mean_Rate <- mean(IMDB_Series$Rate)
median_Rate <- median(IMDB_Series$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB_Series$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB_Series$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB_Series, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB_Series") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB_Series, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB_Series") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```
Result : Calculated the summary statistics and plotted the distribution of rate using histogram and density plot.

## For both Film & Series:
```{r}
library(ggplot2)
library(plotly)



# Plot films and series on the same scatter plot
PVR <- ggplot() +
  # Films
  geom_point(data = IMDB_Film, aes(x = Votes, y = Rate, color = "Film"), size = 0.5) +
  # TV Series
  geom_point(data = IMDB_Series, aes(x = Votes, y = Rate, color = "TV Series"), size = 0.5) +
  # Add x and y axis labels
  labs(x = "Votes", y = "IMDB Rating") +
  # Add title
  ggtitle("IMDB Rating vs Votes for Films and TV Series") +
  # Add legend
  scale_color_manual(name = "Type", values = c("Film" = "#A90500", "TV Series" = "#0012A9"))

ggplotly(PVR)

```
Result : Plotted both film & Series using Scatter plot.




## For Genre:
```{r}

library(tidyr)
df <- IMDB %>% separate_rows(Genre, sep = ",")

tidy_genres <- function(IMDB) {
  df %>%
    separate_rows(Genre, sep = ",")
}

# getting the average rating for each genre
df_avg <- df %>%
  tidy_genres() %>%
  group_by(Genre) %>%
  summarise(avg_rating = mean(Rate))

# creating a bar plot with different colors for each genre
PGRA <- df_avg %>%
  ggplot(aes(x = Genre, y = avg_rating, fill = Genre)) +
  geom_col() +
  scale_fill_hue(name = "Genre") +
  labs(title = "Average Rating by Genre",
       x = "Genre",
       y = "Average Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplotly(PGRA)

```
Result : Average rating and bar plot was calculated for each genre.

## 
```{r}

df_tidy <- df %>%
  tidy_genres()

genre_colors <- c("Action" = "#FFA500", "Adventure" = "#FFC0CB", "Thriller" = "#FFD700",
                  "Crime" = "#00FFFF", "Drama" = "#4169E1", "Sci-Fi" = "#9400D3",
                  "Comedy" = "#32CD32", "Sport" = "#FF69B4", "Horror" = "#FF4500",
                  "Mystery" = "#8B008B")


# create the box plot
PGR <- ggplot(df_tidy, aes(x = Genre, y = Rate)) +
  geom_boxplot() +
  scale_fill_manual(values = genre_colors) +
  labs(title = "Distribution of Ratings by Genre",
       x = "Genre",
       y = "Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplotly(PGR)


```



```{r}
library(ggplot2)


genre_colors <- c("Action" = "#FFA500", "Adventure" = "#FFC0CB", "Thriller" = "#FFD700",
                  "Crime" = "#00FFFF", "Drama" = "#4169E1", "Sci-Fi" = "#9400D3",
                  "Comedy" = "#32CD32", "Sport" = "#FF69B4", "Horror" = "#FF4500",
                  "Mystery" = "#8B008B")

# create box plot
ggplot(data = IMDB, aes(x = Certificate, y = Rate)) +
  geom_boxplot() +
  scale_fill_manual(values = genre_colors)+
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Certificate",
       x = "Certificate",
       y = "IMDB Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```



```{r}
PTR <- ggplot(data = IMDB, aes(x = Type, y = Rate, fill = Type)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Type",
       x = "Type",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9"))
ggplotly(PTR)
```


```{r}
library(ggplot2)
library(plotly)

# create scatter plot
p <- ggplot(data = IMDB, aes(x = Duration, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Duration",
       x = "Duration (minutes)",
       y = "IMDB Rating")

# convert ggplot to plotly object
ggplotly(p)

```


```{r}
library(ggplot2)
library(plotly)

# create scatter plot
p <- ggplot(data = IMDB, aes(x = Votes, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB  Rating vs. Votes",
       x = "Votes",
       y = "IMDB Rating")

# convert ggplot to plotly object
ggplotly(p)

```



```{r}

library(ggplot2)
library(plotly)

# create scatter plot
p <- ggplot(data = IMDB_Series, aes(x = Episodes, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB Series Rating vs. Episodes",
       x = "Episodes",
       y = "IMDB Series Rating")

# convert ggplot to plotly object
ggplotly(p)

```






```{r}
# create scatter plot
ggplot(data = IMDB, aes(x = Rate, y = Nudity)) +
  geom_point(aes(color = "Nudity")) +
  
  # add other scatter plots
  geom_point(aes(x = Rate, y = Violence, color = "Violence")) +
  geom_point(aes(x = Rate, y = Profanity, color = "Profanity")) +
  geom_point(aes(x = Rate, y = Alcohol, color = "Alcohol")) +
  geom_point(aes(x = Rate, y = Frightening, color = "Frightening")) +
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Content Ratings",
       x = "IMDB Rating",
       y = "Content Rating") +
  
  # add legend
  scale_color_manual(name = "Content Rating",
                     values = c(Nudity = "red",
                                Violence = "blue",
                                Profanity = "green",
                                Alcohol = "purple",
                                Frightening = "orange"))

```









```{r}
library(ggcorrplot)

library(dplyr)

# Select relevant numeric variables for correlation matrix
numeric_vars <- IMDB %>% 
  select_if(is.numeric)
# Compute the correlation matrix
cor_matrix <- cor(numeric_vars)

# Create the heatmap using ggcorrplot
ggcorrplot(cor_matrix, type = "lower", hc.order = TRUE, lab = TRUE)

```



```{r}
PRN <- ggplot(data = IMDB, aes(x = Nudity, y = Rate, fill = Nudity)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Nudity",
       x = "Nudity",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRN)


PRV <- ggplot(data = IMDB, aes(x = Violence, y = Rate, fill = Violence)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Violence",
       x = "Violence",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRV)


PRP <- ggplot(data = IMDB, aes(x = Profanity, y = Rate, fill = Profanity)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Profanity",
       x = "Profanity",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRP)


PRA <- ggplot(data = IMDB, aes(x = Alcohol, y = Rate, fill = Alcohol)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Alcohol",
       x = "Alcohol",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRA)


PRF <- ggplot(data = IMDB, aes(x = Frightening, y = Rate, fill = Frightening)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Frightening",
       x = "Frightening",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRF)

```














```{r}
library(stats)

# Fit the ANOVA model
aov_model <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB)

# Get the ANOVA table
aov_output <- summary(model)

# Print the ANOVA table
print(aov_output)


# This table seems to be the output of an ANOVA (Analysis of Variance) test on the relationship between the different content ratings (Nudity, Violence, Profanity, Alcohol, and Frightening) and some other variable(s) in the dataset.
# 
# The first column lists the different content ratings, the second column shows the degrees of freedom (DF) for each rating, the third column shows the sum of squares (Sum Sq) for each rating, and the fourth column shows the mean sum of squares (Mean Sq) for each rating.
# 
# The fifth column shows the F-value, which is a measure of the variation between the groups relative to the variation within the groups. The larger the F-value, the more significant the relationship between the variable(s) being tested and the content rating.
# 
# The sixth column shows the p-value (Pr(>F)), which represents the probability of observing a F-value as extreme or more extreme than the one obtained, assuming that there is no relationship between the variable(s) being tested and the content rating. The lower the p-value, the more significant the relationship.
# 
# In this table, the variables Violence, Profanity, Alcohol, and Frightening all have p-values less than 0.05, which suggests that there is a statistically significant relationship between each of these variables and the content rating. The variable Nudity has a p-value greater than 0.05, which suggests that there is no significant relationship between this variable and the content rating.
```






```{r}
# Fit the ANOVA model
aov_model_film <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB_Film)

# Get the ANOVA table
aov_film_output <- summary(aov_model_film)

# Print the ANOVA table
print(aov_film_output)
```

```{r}
# Fit the ANOVA model
aov_model_series <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB_Series)

# Get the ANOVA table
aov_series_output <- summary(aov_model_series)

# Print the ANOVA table
print(aov_series_output)
```
```{r}
summary(aov(Rate~Nudity,data=IMDB))
summary(aov(Rate~Nudity,data=IMDB_Film))
summary(aov(Rate~Nudity,data=IMDB_Series))
```

```{r}
summary(aov(Rate~Violence,data=IMDB))
summary(aov(Rate~Violence,data=IMDB_Film))
summary(aov(Rate~Violence,data=IMDB_Series))
```



```{r}
summary(aov(Rate~Profanity,data=IMDB))
summary(aov(Rate~Profanity,data=IMDB_Film))
summary(aov(Rate~Profanity,data=IMDB_Series))
```

```{r}
summary(aov(Rate~Alcohol,data=IMDB))
summary(aov(Rate~Alcohol,data=IMDB_Film))
summary(aov(Rate~Alcohol,data=IMDB_Series))
```


```{r}
summary(aov(Rate~Frightening,data=IMDB))
summary(aov(Rate~Frightening,data=IMDB_Film))
summary(aov(Rate~Frightening,data=IMDB_Series))
```






```{r}
lm_model <- lm(Rate ~ Duration , data = IMDB)

# Get the summary of the regression model
summary(lm_model)
```

```{r}
lm_model <- lm(Rate ~ Duration, data = IMDB)

# Get the summary of the regression model
summary(lm_model)
```

```{r}
lm_model <- lm(Rate ~ Votes, data = IMDB)

# Get the summary of the regression model
summary(lm_model)
```


```{r}
summary(lm(Rate ~ Episodes, data = IMDB_Series))
```


```{r}
chisq.test(IMDB$Rate, IMDB$Violence)


```


