---
title: "EDA"
author: "TEAM SIM"
date: "today"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r init, include=TRUE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='asis',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
library(ggplot2)
library(plotly)
library(tidyr)
library(ggcorrplot)
library(dplyr)
library(stats)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "asis", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

## Reading CSV file:
```{r}
IMDB <- read.csv("IMDB.csv")
```
#### Result : Reads and Assigns the data to a variable called IMDB.


## Histogram and Density plot - Distribution of Rate:
```{r}
# for IMDB whole
# Calculate summary statistics
mean_Rate <- mean(IMDB$Rate)
median_Rate <- median(IMDB$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```


#### Result : Understanding distribution of rate by calculating summary statistics using Histogram and Density plot.

## Subsets:
```{r}
IMDB_Film <- subset(IMDB,IMDB$Type=="Film")
head(IMDB_Film)

IMDB_Series <- subset(IMDB,IMDB$Type == "Series")
head(IMDB_Series)
```


#### Result : Creating two subsets of IMDB, i.e: IMDB_Film & IMDB_Series.


## For Movies:
```{r}
#  for movies
# Calculate summary statistics
mean_Rate <- mean(IMDB_Film$Rate)
median_Rate <- median(IMDB_Film$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB_Film$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB_Film$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB_Film, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB_Film") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB_Film, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB_Film") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```


#### Result : Calculated the summary statistics and plotted the distribution of rate using histogram and density plot.



## For Series:
```{r}
# for series

# Calculate summary statistics
mean_Rate <- mean(IMDB_Series$Rate)
median_Rate <- median(IMDB_Series$Rate)
mode_Rate <- as.numeric(names(sort(table(IMDB_Series$Rate), decreasing = TRUE)[1]))
sd_Rate <- sd(IMDB_Series$Rate)

# Plot the distribution of Rate using a histogram
ggplot(data = IMDB_Series, aes(x = Rate)) +
  geom_histogram(binwidth = 0.5, color = "#000000", fill = "#FFFEA4") +
  ggtitle("Distribution of Popularity on IMDB_Series") +
  xlab("Popularity (Rate)") +
  ylab("Count") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 50, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 250, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 500, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 80, label = paste0("SD: ", round(sd_Rate, 2)))

# Alternatively, plot the distribution of Rate using a density plot
ggplot(data = IMDB_Series, aes(x = Rate)) +
  geom_density(color = "#BFBC00", fill = "#FFFEA4", alpha = 0.3) +
  ggtitle("Distribution of Popularity on IMDB_Series") +
  xlab("Popularity (Rate)") +
  ylab("Density") +
  geom_vline(xintercept = mean_Rate, color = "#0F0069", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = median_Rate, color = "#690000", linetype = "dashed",linewidth = 1) +
  geom_vline(xintercept = mode_Rate, color = "#006907", linetype = "dashed",linewidth = 1) +
  annotate("text", x = mean_Rate + 0.5, y = 0.1, label = paste0("Mean: ", round(mean_Rate, 2)),color="#0F0069") +
  annotate("text", x = median_Rate + 0.5, y = 0.2, label = paste0("Median: ", round(median_Rate, 2)),color="#690000") +
  annotate("text", x = mode_Rate + 0.5, y = 0.3, label = paste0("Mode: ", mode_Rate),color="#006907") +
  annotate("text", x = 6, y = 0.2, label = paste0("SD: ", round(sd_Rate, 2)))

cat("Mean Rate:", mean_Rate, "\n")
cat("Median Rate:", median_Rate, "\n")
cat("Mode Rate:", mode_Rate, "\n")
cat("Standard Deviation of Rate:", sd_Rate, "\n")

```


#### Result : Calculated the summary statistics and plotted the distribution of rate using histogram and density plot.

## For both Film & Series:
```{r}
# Plot films and series on the same scatter plot
PVR <- ggplot() +
  # Films
  geom_point(data = IMDB_Film, aes(x = Votes, y = Rate, color = "Film"), size = 0.5) +
  # TV Series
  geom_point(data = IMDB_Series, aes(x = Votes, y = Rate, color = "TV Series"), size = 0.5) +
  # Add x and y axis labels
  labs(x = "Votes", y = "IMDB Rating") +
  # Add title
  ggtitle("IMDB Rating vs Votes for Films and TV Series") +
  # Add legend
  scale_color_manual(name = "Type", values = c("Film" = "#A90500", "TV Series" = "#0012A9"))

ggplotly(PVR)

```


#### Result : Plotted both film & Series using Scatter plot.




## For Genre:
```{r}
df <- IMDB %>% separate_rows(Genre, sep = ",")

tidy_genres <- function(IMDB) {
  df %>%
    separate_rows(Genre, sep = ",")
}

# getting the average rating for each genre
df_avg <- df %>%
  tidy_genres() %>%
  group_by(Genre) %>%
  summarise(avg_rating = mean(Rate))

# creating a bar plot with different colors for each genre
PGRA <- df_avg %>%
  ggplot(aes(x = Genre, y = avg_rating, fill = Genre)) +
  geom_col() +
  scale_fill_hue(name = "Genre") +
  labs(title = "Average Rating by Genre",
       x = "Genre",
       y = "Average Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplotly(PGRA)

```


#### Result : Average rating and bar plot was calculated for each genre.

## Colours for Each Genre:
```{r}

df_tidy <- df %>%
  tidy_genres()

genre_colors <- c("Action" = "#FFA500", "Adventure" = "#FFC0CB", "Thriller" = "#FFD700",
                  "Crime" = "#00FFFF", "Drama" = "#4169E1", "Sci-Fi" = "#9400D3",
                  "Comedy" = "#32CD32", "Sport" = "#FF69B4", "Horror" = "#FF4500",
                  "Mystery" = "#8B008B")


# create the box plot
PGR <- ggplot(df_tidy, aes(x = Genre, y = Rate)) +
  geom_boxplot() +
  scale_fill_manual(values = genre_colors) +
  labs(title = "Distribution of Ratings by Genre",
       x = "Genre",
       y = "Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplotly(PGR)


```


#### Result : Colours are assigned to each of the genre to under the analysis results better.

## Box plot for Genre:
```{r}
genre_colors <- c("Action" = "#FFA500", "Adventure" = "#FFC0CB", "Thriller" = "#FFD700",
                  "Crime" = "#00FFFF", "Drama" = "#4169E1", "Sci-Fi" = "#9400D3",
                  "Comedy" = "#32CD32", "Sport" = "#FF69B4", "Horror" = "#FF4500",
                  "Mystery" = "#8B008B")

# create box plot
ggplot(data = IMDB, aes(x = Certificate, y = Rate)) +
  geom_boxplot() +
  scale_fill_manual(values = genre_colors)+
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Certificate",
       x = "Certificate",
       y = "IMDB Rating")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```


#### Result : Plotted a Box plot to understand the analysis on genre better.


```{r}
PTR <- ggplot(data = IMDB, aes(x = Type, y = Rate, fill = Type)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Type",
       x = "Type",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9"))
ggplotly(PTR)
```


#### Result : Plotted a box plot to understand the distribution of ratings by type.

## Duration and IMDB rating:

```{r}
# create scatter plot
p <- ggplot(data = IMDB, aes(x = Duration, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Duration",
       x = "Duration (minutes)",
       y = "IMDB Rating")

# convert ggplot to plotly object
ggplotly(p)

```


#### Result : Plotted a scatter plot with a regression line to understand the relationship between IMDB rating and duration.


## IMDB Rating and votes:
```{r}
# create scatter plot
p <- ggplot(data = IMDB, aes(x = Votes, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB  Rating vs. Votes",
       x = "Votes",
       y = "IMDB Rating")

# convert ggplot to plotly object
ggplotly(p)

```


#### Result : Plotted a scatter plot with a regression line to understand the relationship between IMDB rating and votes.

## IMDB Series rating and Episodes:
```{r}
# create scatter plot
p <- ggplot(data = IMDB_Series, aes(x = Episodes, y = Rate)) +
  geom_point(size = 0.5) +
  
  # add regression line
  geom_smooth(method = "lm", se = FALSE) +
  
  # add axis labels and title
  labs(title = "IMDB Series Rating vs. Episodes",
       x = "Episodes",
       y = "IMDB Series Rating")

# convert ggplot to plotly object
ggplotly(p)

```


#### Result : Plotted a scatter plot with a regression line to understand the relationship between IMDB series rating and episodes.




## IMDB rating and content rating:
```{r}
# create scatter plot
ggplot(data = IMDB, aes(x = Rate, y = Nudity)) +
  geom_point(aes(color = "Nudity")) +
  
  # add other scatter plots
  geom_point(aes(x = Rate, y = Violence, color = "Violence")) +
  geom_point(aes(x = Rate, y = Profanity, color = "Profanity")) +
  geom_point(aes(x = Rate, y = Alcohol, color = "Alcohol")) +
  geom_point(aes(x = Rate, y = Frightening, color = "Frightening")) +
  
  # add axis labels and title
  labs(title = "IMDB Rating vs. Content Ratings",
       x = "IMDB Rating",
       y = "Content Rating") +
  
  # add legend
  scale_color_manual(name = "Content Rating",
                     values = c(Nudity = "red",
                                Violence = "blue",
                                Profanity = "green",
                                Alcohol = "purple",
                                Frightening = "orange"))

```


#### Result : Plotted a scatter plot to understand the relationship between IMDB rating and content ratings.







## Correlation heat map:
```{r}
# Select relevant numeric variables for correlation matrix
numeric_vars <- IMDB %>% 
  select_if(is.numeric)
# Compute the correlation matrix
cor_matrix <- cor(numeric_vars)

# Create the heatmap using ggcorrplot
ggcorrplot(cor_matrix, type = "lower", hc.order = TRUE, lab = TRUE)

```


#### Results : Computed the correlation matrix and created a heat map using ggcorrplot.

## Ratings and the Characteristics of Film & Series:
```{r}
PRN <- ggplot(data = IMDB, aes(x = Nudity, y = Rate, fill = Nudity)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Nudity",
       x = "Nudity",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRN)


PRV <- ggplot(data = IMDB, aes(x = Violence, y = Rate, fill = Violence)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Violence",
       x = "Violence",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRV)


PRP <- ggplot(data = IMDB, aes(x = Profanity, y = Rate, fill = Profanity)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Profanity",
       x = "Profanity",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRP)


PRA <- ggplot(data = IMDB, aes(x = Alcohol, y = Rate, fill = Alcohol)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Alcohol",
       x = "Alcohol",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRA)


PRF <- ggplot(data = IMDB, aes(x = Frightening, y = Rate, fill = Frightening)) + 
  geom_boxplot() +
  labs(title = "Distribution of Ratings by Frightening",
       x = "Frightening",
       y = "Rating") +
  scale_fill_manual(values = c("#A90500", "#0012A9","#C00CC2","#15C20C"))
ggplotly(PRF)

```


#### Results : Plotted the Box plot to understand the Distribution of Rating by nudity, violence, profanity, alcohol, frightening.















### Analysis of Variance


## Anova for Content variables with both Film and Series

```{r}
aov_model <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB)

aov_output <- summary(aov_model)

print(aov_output)
```

#### The variables of Violence, Profanity, Alcohol, and Frightening have a significant difference between them, while the Nudity variable does not have a significant difference. This table provides valuable insights into the differences between the variables in the dataset.



## Anova for Content variables with Film

```{r}
aov_model_film <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB_Film)

aov_film_output <- summary(aov_model_film)

print(aov_film_output)
```
#### From the table, we can see that all of the variables have a significant difference between them, with Alcohol and Frightening having the highest F-values and the lowest p-values, indicating that the difference between their average values is the most significant.

#### The Nudity, Violence, and Profanity variables also have a significant difference, but not as significant as Alcohol and Frightening.


## Anova for Content variables with Series


```{r}
aov_model_series <- aov(Rate ~ Nudity + Violence + Profanity + Alcohol + Frightening, data = IMDB_Series)

aov_series_output <- summary(aov_model_series)

print(aov_series_output)
```
#### From the table, we can see that all of the variables have a significant difference between them, with Violence having the highest F-value and the lowest p-value, indicating that the difference between its average value and the others is the most significant.

#### The other variables of Nudity, Profanity, Alcohol, and Frightening also have a significant difference, but not as significant as Violence.


## Anova for Nudity with Both (Film and series), Film & Series 
```{r}
summary(aov(Rate~Nudity,data=IMDB))
summary(aov(Rate~Nudity,data=IMDB_Film))
summary(aov(Rate~Nudity,data=IMDB_Series))
```
####Film and Series : From the table, we can see that there is no significant difference between the average values of Nudity in the dataset. This is because the p-value is higher than the commonly used alpha level of 0.05.

#### Film : From the table, we can see that the p-value is less than the commonly used alpha level of 0.05, which indicates that there is a significant difference between the average values of Nudity in the dataset. The asterisks (**), next to the p-value, indicate the level of significance; in this case, two asterisks indicate a p-value less than 0.01.

#### Series: From the table, we can see that the p-value is less than the commonly used alpha level of 0.05, which indicates that there is a significant difference between the average values of Nudity in the dataset.The asterisk (*) next to the p-value indicates the level of significance, where a single asterisk indicates a p-value less than 0.05.



## Anova for Violence with Both (Film and series), Film & Series 


```{r}
summary(aov(Rate~Violence,data=IMDB))
summary(aov(Rate~Violence,data=IMDB_Film))
summary(aov(Rate~Violence,data=IMDB_Series))
```
#### Film and Series : In this case, the variable "Violence" has a significant effect on the outcome variable, as the p-value is less than 0.05 (indicated by "*"). Therefore, we reject the null hypothesis that the variable "Violence" has no effect on the outcome variable.

#### Film : The table indicates that there is a significant difference between groups (p < 0.01), meaning that the "Violence" variable varies significantly depending on Rate

#### Series : The results indicate that there is a significant effect of "Violence" on "Rate", as evidenced by the very small p-value (7.4e-06) and the significant F value (8.95). Therefore, we can conclude that "Violence" has a significant impact on the ratings of TV series in this dataset.

#### For the variable Violence, there is a statistically significant effect on Rate in all three datasets (p < 0.01), indicating that the amount of violence in a movie or TV show is related to the audience's rating of it.


```{r}
summary(aov(Rate~Profanity,data=IMDB))
summary(aov(Rate~Profanity,data=IMDB_Film))
summary(aov(Rate~Profanity,data=IMDB_Series))
```

#### These are the ANOVA results for the relationship between "Rate" and "Profanity" in the "IMDB", "IMDB_Film", and "IMDB_Series" datasets. In all three datasets, the "Profanity" variable is significant at the p < .01 level, indicating a significant relationship between the amount of profanity in a movie or series and its rating.

```{r}
summary(aov(Rate~Alcohol,data=IMDB))
summary(aov(Rate~Alcohol,data=IMDB_Film))
summary(aov(Rate~Alcohol,data=IMDB_Series))
```
#### For the variable Alcohol, there is a statistically significant effect on Rate in all three datasets (p < 0.01), indicating that the portrayal of alcohol in movies and TV shows affects how the audience rates them.

```{r}
summary(aov(Rate~Frightening,data=IMDB))
summary(aov(Rate~Frightening,data=IMDB_Film))
summary(aov(Rate~Frightening,data=IMDB_Series))
```







## Liner Regression Model
### LM model for Rate and Duration in Film and Series

```{r}
lm_model <- lm(Rate ~ Duration , data = IMDB)

# Get the summary of the regression model
print(summary(lm_model))
```


#### The intercept is 7.419, which represents the estimated mean rating when the duration is zero. The coefficient for 'Duration' is -0.004764, which indicates that the estimated mean rating decreases by 0.004764 for every additional minute of duration.

#### The p-value for the coefficient of 'Duration' is less than 2e-16, which indicates that the relationship between 'Duration' and 'Rate' is statistically significant. The R-squared value is 0.028, which indicates that only 2.8% of the variability in 'Rate' can be explained by 'Duration'.

#### The F-statistic is significant with a p-value of less than 2e-16, which confirms that the model is a good fit for the data. The residual standard error is 1.02, which indicates the average difference between the observed 'Rate' and the predicted 'Rate' values is 1.02 units.











### LM model for Rate and Votes in Film and Series


```{r}
lm_model <- lm(Rate ~ Votes, data = IMDB)

# Get the summary of the regression model
summary(lm_model)
```
#### The regression model for Rate and Votes shows that the p-value for the regression coefficient is less than 0.05, indicating that there is a statistically significant relationship between the two variables. The coefficient estimate for Votes is 1.49e-06, indicating that for every additional vote, the rate increases by approximately 1.49e-06 units. The adjusted R-squared value is 0.0989, indicating that only 9.89% of the variation in Rate is explained by the variation in Votes. Overall, while there is a statistically significant relationship between the two variables, Votes alone does not explain much of the variation in Rate.


### LM model for Rate and Episodes in Series



```{r}
summary(lm(Rate ~ Episodes, data = IMDB_Series))
```



#### This is a simple linear regression model with one predictor variable, Episodes, and one response variable, Rate. The coefficient for Episodes is -2.62e-04, indicating that for each additional episode, the predicted Rate score decreases by approximately 0.00026. The intercept is 7.70e+00, indicating that if a series had zero episodes, the predicted Rate score would be 7.70.

#### The p-value for the coefficient of Episodes is less than 0.05, suggesting that the relationship between Episodes and Rate is statistically significant. The R-squared value is 0.075, indicating that the model explains only a small proportion of the variation in the data. The residual standard error is 0.812, indicating that the model's predictions are typically off by about 0.81 on the Rate scale.







